Object-based Auditory Scenes Similarity Retrieval and Classification With Scattering Transforms

### 2016-07-08 paper/structureScene.tex
include draft histogram fig in section IV.3
update number of instances with new train/test split

@@

\subsection{Early vs. late temporal integration}
Owing to the scarcity of salient events in many natural \ml{sound scenes soundscapes est un modele de perception de la scene}, fine-grained classification of auditory scenes is only made
possible by integrating signal information over a long temporal context.
Indeed, whereas a few seconds are often sufficient to recognize a speaker,
a musical instrument, or a genre, it may require up to 30 seconds
to disambiguate auditory scenes which share part of their semantic content, \eg a train from a subway station or a quiet street from a park.
Depending on whether aggregation is performed in feature space or in decision space, the corresponding method is referred to as early or late integration.

@@

The principal drawback of early integration is that it drastically reduces the number of training instances at the classifier stage, down to one per auditory scene -- if data augmentation is not considered.
In the context of the DCASE 2013 dataset, this corresponds to merely $10$ training instances per class, and $100$ instances overall, hence an increase in variance in statistical estimation and a risk of overfitting.
On the contrary, a late integration scheme for $T=188\textrm{ ms}$ would yield $128$ instances per auditory scene, resulting in $12800$ instances overall.
\vl{Update number of instances with new train / test split}
However, many of these instances may be silent or lack any salient properties of the category they are assigned to, hence an increase in bias and a risk of underfitting.
In short, early and late integration methods lie at opposite ends of the bias-versus-variance statistical tradeoff. We refer to \cite{Joder2009} for a comprehensive review of this problematic in the context of musical instrument recognition.

>>>>

\begin{figure}
\begin{center}
\setlength{\unitlength}{1cm}
\begin{picture}(5,2)
 \put(-1.5,0.0){\includegraphics[height=2cm,width=3.5cm]{feature_histogram.png}}
 \put(2.5,0.0){\includegraphics[height=2cm,width=3.5cm]{feature_histogram_logcompressed.png}}
\end{picture}
\caption{
\label{fig:histograms}
\vl{we should discuss color schemes and axis labels}}
\end{center}
\end{figure}

@@

\subsection{Early vs. late temporal integration}
Owing to the scarcity of salient events in many natural scenes,
fine-grained classification is only made
possible by integrating signal information over a long temporal context.
Indeed, whereas a few seconds are often sufficient to recognize a speaker,
a musical instrument, or a genre, it may require up to 30 seconds
to disambiguate auditory scenes which share part of their semantic content, \eg a train from a subway station or a quiet street from a park.
Depending on whether aggregation is performed in feature space or in decision space, the corresponding method is referred to as early or late integration.

@@

The principal drawback of early integration is that it drastically reduces the number of training instances at the classifier stage, down to one per auditory scene -- if data augmentation is not considered.
In the context of the DCASE 2013 dataset, this corresponds to merely $8$ training instances per class, and $80$ instances overall, hence an increase in variance in statistical estimation and a risk of overfitting.
On the contrary, a late integration scheme for $T=188\textrm{ ms}$ would yield $128$ instances per auditory scene, resulting in $10240$ instances overall.
However, many of these instances may be silent or lack any salient properties of the category they are assigned to, hence an increase in bias and a risk of underfitting.
In short, early and late integration methods lie at opposite ends of the bias-versus-variance statistical tradeoff. We refer to \cite{Joder2009} for a comprehensive review of this problematic in the context of musical instrument recognition.
